A tutorial on Generalised Additive Mixed Effects Models for bilingualism research

### 2024-06-12 manuscript/manuscript.qmd

```{r}
#| label: gam-2-preds
#| warning: false
# Get model predictions for 'proficiency', assign them to 'gam_2_preds'
gam_2_preds <- predict_gam(
  gam_2, length_out = 25,
  series = "proficiency",
  exclude_terms = c("s(subj)")
)
```

@@

```{r}
#| label: fig-gam-2-preds-t
#| fig-cap: "Predicted accuracy score as a function of time, from a GAM."
# Plot predictions
plot(gam_2_preds_t) +
  ylim(20, 45)
```

>>>>

```{r}
#| label: gam-2-preds
#| warning: false

# Get model predictions for 'proficiency', assign them to 'gam_2_preds'
gam_2_preds <- predict_gam(
  gam_2, length_out = 25,
  series = "proficiency",
  exclude_terms = c("s(subj)")
)
```

@@

```{r}
#| label: fig-gam-2-preds-t
#| fig-cap: "Predicted accuracy score as a function of time, from a GAM."

# Plot predictions
plot(gam_2_preds_t) +
  ylim(20, 45)
```
